Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 README.Rmd
decided not to keep paper.R file in main directory (only in submission) so no confusion with code used in paper (only in Rnw)

- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
- `figure-compression.R` contains R code for compressing the static figure used in the manuscript
- `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.

>>>>

- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
- `figure-compression.R` contains R code for compressing the static figure used in the manuscript
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
